SVG: The Paper

### 2022-04-19 Analysis/index.Rmd
adding hex maps

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

>>>>

ggplot(d, aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c() -> plt_all

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c() -> plt_med

plt_all 
plt_med
